Lambda extraction summary

### 2016-02-19 paper-lambda/summary/lambda.tex

In this document we briefly summarise the results of the Higgs trilinear coupling extraction exercise, for the case of the 14TeV HL-LHC and
the 100TeV FCC.
\subsection{Cross-section variation with $\lambda$}
These figures demonstrate the variation of the $HH$ cross-section with the value of the Higgs trilinear coupling, after processing through our analysis
but before the application of the MVA. Results here are given for the resolved~(Fig. \ref{fig:resXsec}), intermediate~(Fig. \ref{fig:interXsec}) and boosted ~(Fig. \ref{fig:boostXsec}) topologies. All figures are shown for the 14TeV LHC on the left, and 100TeV FCC on the right.

@@

\newpage
\subsection{Trilinear extraction - $\chi2$ profiles}

>>>>

In this document we briefly summarise the results of the Higgs trilinear coupling extraction exercise, for the case of the 14TeV HL-LHC and
the 100TeV FCC.
\section{Cross-section variation with $\lambda$}
These figures demonstrate the variation of the $HH$ cross-section with the value of the Higgs trilinear coupling, after processing through our analysis
but before the application of the MVA. Results here are given for the resolved~(Fig. \ref{fig:resXsec}), intermediate~(Fig. \ref{fig:interXsec}) and boosted ~(Fig. \ref{fig:boostXsec}) topologies. All figures are shown for the 14TeV LHC on the left, and 100TeV FCC on the right.

@@

\newpage
\section{Trilinear extraction - $\chi2$ profiles}
